---
title: "Analysis of Taste Adaptation Study"
output: html_document
editor_options: 
  chunk_output_type: console
bibliography: 4b_analysis.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(geepack)
# library(lme4)
library(geex)
source("4a_create_analysis_datasets.r")
```
*PRELIMARY RESULTS*

# Methods

## Outcomes

* primary: changes in suprathreshold intensity
* secondary: changes in detection and recognition thresholds

## Sample Size and Power

The sample size for this pilot study was based on a model-based simulation study of changes in suprathreshold intensity from day 0 to day 5 of fasting. The target of the simulation was estimating 90\% confidence intervals instead of power. This approach for justifying pilot study sample size is recommended when little is known about the parameter(s) of interest over a hypothesis testing approach [@hertzog2008; @moore2011; @lee2014].

## Statistical Analyses

Demographics, baseline characteristics, and fasting lengths were described by appropriate statistical and graphical summaries.

For analysis of suprathreshold intensities, we excluded the zero concentrations as only `r supra_analysis %>% filter(conc ==0, response > 0 ) %>% nrow()` of the `r supra_analysis %>% filter(conc ==0) %>% nrow()` tests had a value other than zero at this concentration. The mean and standard deviation of responses were computed for each assay, concentration, and time point. To estimate the marginal effect of days since start of fast on suprathrehold intensity, a Generalized Estimating Equation (GEE) [@liang1986] model of $log(1 + \text{response})$ was fit with terms for days since start of fast, $log_{10}(\text{concentration})$, and their interaction. Models were fit separately within each taste. Model estimates were transformed back to the original scale are presented with point-wise 90\% confidence intervals.

Recognition and detection thresholds were summarized by mean and standard deviations for each assay and time point. TODO: modelling

Statistical analyses were done in `r R.version.string` [@rcore] using the geepack [@geepack], geex [@geex], and ggplot2 [@ggplot2] packages.

# Results

TODO: describe subject characteristics 

```{r study_n}
counts <- 
  supra_analysis %>%
  ungroup() %>%
  distinct(record_id, time) %>%
  group_by(time) %>%
  count()
```

All subjects completed the assays at the start of fast, day 5, and end of fast + 3 days. Only `r counts$n[3]` subjects completed the assays at the end of fast timepoint.

```{r, results = "asis"}
fast_length <- 
  supra_analysis %>% 
  ungroup() %>%
  select(record_id, time, days) %>%
  filter(time == 4) %>%
  group_by(record_id) %>%
  summarise(fast_length = max(days) - 3)

clinical_summary <- 
  clinical %>%
  filter(time == 1) %>%
  select(
    record_id, height, weight, bmi, 
    systolic_blood_pressure, diastolic_blood_pressure
  ) %>%
  left_join(
    fast_length, by = "record_id"
  ) %>%
  left_join(
    demographics, by = "record_id"
  ) %>%
  mutate(
    record_id = as.character(record_id)
  ) %>%
  mutate(
    male = (gender == 1) * 1
  ) 

fvars <- 
  clinical_summary %>%
  select_if(is.factor) %>%
  summarise_all(
    .funs = list(tab = ~ list(table(.)))
  )


clinical_summary %>%
  select_if(is.numeric) %>%
  tidyr::gather(key = "key", value = "value") %>%
  group_by(key) %>%
  summarise(
    mean   = mean(value, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    sd     = sd(value, na.rm = TRUE),
    iqr    = IQR(value, na.rm = TRUE)
  ) %>%
  knitr::kable(
    digits = 2
  )

```

## Changes in Supratheshold Intensity

```{r supra_table, results = 'asis'}
supra_analysis %>%
  ungroup %>% 
  # filter(conc > 0) %>%
  group_by(assay_taste, conc, time) %>%
  summarise(
    x = sprintf("%.1f (%.2f)", mean(response), sd(response))
  ) %>% 
  tidyr::spread(
    key = time,
    value = x
  ) %>%
  ungroup() %>%
  mutate(
   assay_taste = factor(
      assay_taste, 
       levels = c("nacl", "sucr"),
       labels = c("NaCL", "Sucrose")),
  ) %>%
  knitr::kable(
    align = c("l", "l", rep("c", 4)),
    col.names = c("Assay", "Concentration", 
                  paste(c("Start of Fast",
                          "Day 5", "End of fast", "End of fast + 3 days"),
                        paste0("(n=", counts$n, ")"))),
    caption = "Mean (Standard deviation) of Suprathreshold repsonses at timepoints"
  )
  

```

```{r supra_model_dt}
supra_model_dt <-
  supra_analysis %>%
  ungroup %>% 
  filter(conc > 0) %>%
  mutate(
    y = log1p(response),
  ) %>%
  select(y, days, assay_taste, time, c = conc, id = record_id) %>%
  arrange(id) %>%
  group_nest(assay_taste) %>%
  mutate(
    data_pre_to_5 = purrr::map(data, ~ .x %>% filter(time %in% c(1, 2)) )
  )
```

```{r supra_model}
geex_correct <- function(data, model){
  f <- geex::grab_psiFUN(object = model, data = data)
  function(theta){
    f(theta)
  }
}

gee_fit1 <- function(data){
  geepack::geeglm(
    formula = y ~ days * log10(c),
    id   = id,
    data = data, 
    family = gaussian(link = 'identity'))
}

mest <- function(fitter, data){
  m <- fitter(data)
  m_estimate(
    data        = data,
    units       = 'id',
    estFUN      = geex_correct,
    outer_args  = list(model = m),
    corrections = list(fay = correction(
      FUN = fay_bias_correction,
      b   = 0.75)),
    compute_roots  = FALSE,
    roots     = coef(m))
}

get_est <- function(fit, ndays = 17, conc = c(50, 100, 200)){

  entries <- 
  expand.grid(
    days = 0:ndays, 
    conc = conc
  )
  
  # Contrast matrix
  # TODO: This is hardcoded based on the model specification!!
  make_L <- function(d, c){
    c(1, d, log10(c), d * log10(c))
  }
  
  L <- t(apply(entries, 1, function(x) { make_L(x[1], x[2]) }))
  
  cbind(
    entries,
    est = L %*% coef(fit),
    se  = sqrt(diag(L %*% vcov(fit) %*% t(L)))
  )
}

get_est_diff <- function(fit, ndays = 10, conc = c(50, 100, 200)){
  
  # Contrast matrix
  # TODO: This is hardcoded based on the model specification!!
  make_L <- function(d, c){
    c(1, d, log10(c), d * log10(c))
  }
  
  # Use delta method to obtain standard errors:
  # h(theta) = expm1(X_10 %*% theta) - expm1(X_0 %*% theta)
  # h'(theta) = 
  #  ( 
  #     exp(X_10 %*% theta) - exp(X_0 %*% theta)
  #     10   * exp(X_10 %*% theta) 
  #     conc * (exp(X_10 %*% theta) - exp(X_0 %*% theta))
  #     10   * conc * exp(X_10 %*% theta) 
  # )
  theta <- coef(fit)
  sigma <- vcov(fit)
  est <- numeric(length(conc))
  se  <- numeric(length(conc))
  
  # Obtaining for each concentration independently; though this could be done
  # all at once
  for(i in seq_along(conc)){
    Ln <- make_L(ndays, conc[i])
    L0 <- make_L(0, conc[i])
    
    J <- (Ln %*% exp(Ln %*% theta)) - (L0 %*% exp(L0 %*% theta))
    V <- t(J) %*% vcov(fit) %*% J
    
    est[i] <- expm1(Ln %*% theta) - expm1(L0 %*% theta)
    se[i]  <- sqrt(V)
  }
  
  tibble::tibble(
    conc,
    est = est,
    se  = se
  )
}

supra_model_dt %>%
  mutate(
    fit_alldays = purrr::map(
      .x = data,
      .f = ~ mest(gee_fit1, .x)
    ),
    est_alldays = purrr::map2(
      .x = fit_alldays, 
      .y = assay_taste,
      .f = ~ {
        if(.y == "sucr") {
          get_est(.x, conc = c(100, 200, 400))
        } else {
          get_est(.x)
        } }
    ),
   est_diff_day10 = purrr::map2(
      .x = fit_alldays, 
      .y = assay_taste,
      .f = ~ {
        if(.y == "sucr") {
          get_est_diff(.x, ndays = 10, conc = c(100, 200, 400))
        } else {
          get_est_diff(.x, ndays = 10)
        } })
    
  ) -> 
  supra_fits

supra_fits %>%
  select(
    assay_taste, est_alldays
  ) %>%
  tidyr::unnest(cols = c(est_alldays)) %>%
  mutate(
    conf_lo = est - qnorm(.9) * se,
    conf_hi = est + qnorm(.9) * se,
    est     = expm1(est),
    conf_lo = expm1(conf_lo),
    conf_hi = expm1(conf_hi)
  ) -> 
  supra_model_res

supra_changes <- 
  supra_fits %>%
  select(
    assay_taste, est_diff_day10
  ) %>%
  tidyr::unnest(cols = c(est_diff_day10)) %>%
  mutate(
    conf_lo = est - qnorm(.9) * se,
    conf_hi = est + qnorm(.9) * se,
    est     = est
  ) %>%
  mutate(label = sprintf("%.1f (%.1f, %.1f)", est, conf_lo, conf_hi)) 


supra_nacl_changes <- filter(supra_changes, assay_taste == "nacl") %>% pull(label)
supra_sucr_changes <- filter(supra_changes, assay_taste == "sucr") %>% pull(label)
```

Figure `\@ref(fig:supra_days)` displays changes in suprathreshold intensity for salt and sweet taste during the study period for all subjects along with the estimated GEE model. Responses are highly variable, especially between subjects (Table `\@ref(table1)`), but show a general trend of increasing response to salt and descreasing response to sweet. For example, the GEE model estimates that after 10 days of fasting the average salt taste response increases by `r supra_nacl_changes %>% glue::glue_collapse(sep = ", ", last = ", and ")` for the 50, 100, and 200 mg/L concentrations, respectively. Over the same time span, the average sweet taste response is estimated to change by `r supra_sucr_changes %>% glue::glue_collapse(sep = ", ", last = ", and ")` for each concentration respectively. 


```{r supra_days}
supra_plot <- supra_analysis %>%
  filter(conc != 0) %>%
  ungroup() %>%
  mutate(
    assay_taste = factor(
      assay_taste, 
       levels = c("nacl", "sucr"),
       labels = c("NaCL", "Sucrose")),
    conc_label  = factor(
      conc, 
      levels = sort(unique(conc)),
      labels = sprintf("%s mg/L", sort(unique(conc))),
      ordered = TRUE)
  )

conc_labs <- distinct(supra_plot, assay_taste, conc, conc_rank, conc_label)

supra_model_plot <- 
  supra_model_res %>%
  mutate(
    assay_taste = factor(
      assay_taste, 
       levels = c("nacl", "sucr"),
       labels = c("NaCL", "Sucrose"))
  ) %>% 
  left_join(
    conc_labs,
    by = c("assay_taste", "conc")
  )

supra_changes_plot <- 
  supra_changes %>%
  mutate(
    assay_taste = factor(
      assay_taste, 
       levels = c("nacl", "sucr"),
       labels = c("NaCL", "Sucrose"))
  ) %>% 
  left_join(
    conc_labs,
    by = c("assay_taste", "conc")
  ) %>%
  left_join(
    y = supra_model_plot %>% filter(days == 10) %>%
      select(assay_taste, conc, ypos = est),
    by = c("assay_taste", "conc")
  ) %>%
  left_join(
    y = supra_model_plot %>% filter(days == 0) %>%
      select(assay_taste, conc, y0pos = est),
    by = c("assay_taste", "conc")
  )
  

```

```{r supra_plot , fig.height = 5, fig.width= 8}
ggplot(
  data  = supra_plot, 
  mapping = aes(x = days, y = response)
  ) + 
  geom_hline(
    yintercept = 0, color = "grey50", size = 0.5
  ) +
  geom_line(
    aes(group = record_id),
    color = "grey80",
    size = .3) + 
  geom_point(
    color = "grey80",
    size = 0.3
  ) + 
  geom_line(
    data = supra_model_plot,
    aes(x = days, y = est, color = assay_taste),
    inherit.aes = FALSE
  ) + 
  geom_ribbon(
    data = supra_model_plot,
    aes(x = days, ymin = conf_lo, ymax = conf_hi, fill = assay_taste),
    alpha = 0.25,
    inherit.aes = FALSE
  ) +
  geom_segment(
    data = supra_changes_plot,
    aes(x = 0, xend = 10, y = y0pos, yend = y0pos),
    linetype = "dotted",
    size = .2, color = "grey20"
  ) + 
  geom_segment(
    data = supra_changes_plot,
    aes(x = 10, xend = 10, y = ypos, yend = y0pos),
    linetype = "dotted",
    size = .2, color = "grey20"
  ) + 
  geom_text(
    data = supra_changes_plot,
    aes(x = 10, y = ypos, label = label),
    hjust = 0, vjust = 0, size = 2, color = "grey10"
  ) + 
  geom_text(
    data = conc_labs,
    aes(x = 2, y = 5, label = conc_label),
    hjust = 0, size = 2.5, color = "grey40"
  ) + 
  facet_grid(assay_taste ~ conc_rank) + 
  scale_y_continuous(
    expand = c(0, 0)
  ) + 
  scale_color_manual(
    guide = FALSE,
    values = c("#7b4244", "#60e9dc")
  ) +
  scale_fill_manual(
    guide = FALSE,
    values = c("#7b4244", "#60e9dc")
  ) +
  labs(
    title = "Changes in suprathreshold intensity",
    x = "Days since start of fast",
    y = "Response",
    caption = "Each line is a single subject's trajectory.\nColored lines show GEE model fit with pointwise 90% confidence intervals.\nValue is estimated average change from Day 0 to 10 with 90% confidence interval."
  ) + 
  theme_classic() +
  theme(
    strip.background = element_blank(),
    # strip.background.y = element_blank(),
    strip.text.x  = element_blank(), 
    strip.text.y  = element_text(angle = 0),
    axis.line.x   = element_blank(),
    axis.line.y   = element_line(color = "grey50", size = 0.5),
    axis.ticks.y  = element_line(color = "grey50", size = 0.1),
    axis.ticks.x  = element_line(color = "grey50", size = 0.1),
    axis.text     = element_text(size = 6),
    axis.title.y  = element_text(size = 8),
    axis.title.x  = element_text(size = 8),
    plot.caption  = element_text(size = 6)
  )
```

## Changes in Detection/Recognition Thresholds


```{r dtrt_bytime}
dtrt_dt <- dtrt_thresholds %>% 
  ungroup() %>%
  select(-dtp, -rtp, -taste_order) %>%
  tidyr::gather(key = "type", value = "conc", 
                -record_id, -time, -days, -assay_taste) %>%
  mutate(
    assay_taste = factor(
        assay_taste, 
         levels = c("nacl", "sucr"),
         labels = c("NaCL", "Sucrose")),
    type = factor(
      type,
      levels = c("dt", "rt"),
      labels = c("Detection", "Recognition")
    )
  ) %>%
  group_by(assay_taste, type, record_id) %>%
  arrange(time, .by_group = TRUE) %>%
  mutate(
    conc2 = log1p(conc) - lag(log1p(conc), default = NA)
  )
```

```{r dtrt_table}
dtrt_dt %>%
  group_by(assay_taste, time, type) %>%
  summarise(
    x = sprintf("%.1f (%.2f)", mean(conc), sd(conc))
  ) %>% 
  tidyr::spread(
    key = time,
    value = x
  ) %>%
  knitr::kable(
    align = c("l", "l", rep("c", 4)),
    col.names = c("Assay", "Threshold", 
                  "Start of Fast",
                   "Day 5", "End of fast", "End of fast + 3 days"),
    caption = "Mean (Standard deviation) of thresholds at study timepoints"
  )
```

A simple paired t-test between day 0 and end of fast:

```{r dtrt_ttest}
dtrt_dt %>%
  ungroup() %>%
  filter(time %in% c(1, 3)) %>%
  select(-days, -conc2) %>%
  group_by(assay_taste, type) %>%
  tidyr::pivot_wider(
    names_from = time, 
    names_prefix = "time",
    values_from = conc
  ) %>%
  tidyr::nest() %>%
  mutate(
    p_value = purrr::map_dbl(
      .x = data,
      .f = ~ t.test(x = .x[["time1"]], y = .x[["time3"]], paired = TRUE)[["p.value"]])
  ) %>%
  select(
    assay_taste, type, p_value
  )
```

```{r dtrt_plot, fig.height = 5, fig.width= 8}
ggplot(
  data = dtrt_dt,
  aes(x = days, y = log10(conc))
) + 
  geom_hline(
    yintercept = 0, color = "grey50", size = 0.5
  ) +
  geom_point(
    color = "grey80",
    size = 0.8,
    position = position_dodge(width = 1)
  ) + 
  geom_line(
    aes(group = record_id), 
    color = "grey80",
    alpha = .5) + 
  stat_smooth(
    aes(color = assay_taste), 
    method = "lm", se = FALSE) + 
  scale_color_manual(
    guide = FALSE,
    values = c("#7b4244", "#60e9dc")
  ) +
  facet_grid(assay_taste ~ type, scales = "free_y") + 
  labs(
    title = "Changes in Detection/Recognition Thresholds",
    x = "Days since start of fast"
  ) + 
  theme_classic() +
  theme(
    strip.background = element_blank(),
    # strip.background.y = element_blank(),
    # strip.text.x  = element_blank(), 
    strip.text.y  = element_text(angle = 0),
    axis.line.x   = element_blank(),
    axis.line.y   = element_line(color = "grey50", size = 0.5),
    axis.ticks.y  = element_line(color = "grey50", size = 0.1),
    axis.ticks.x  = element_line(color = "grey50", size = 0.1),
    axis.text     = element_text(size = 6),
    axis.title.y  = element_text(size = 8),
    axis.title.x  = element_text(size = 8),
    plot.caption  = element_text(size = 6)
  )
```

```{r dtCorrelations}
baseline_vars <- 
  clinical_summary %>%
  select(record_id, bmi, age, male)

hold_thresholds <- 
  dtrt_thresholds %>%
  filter(time %in% c(1, 4)) %>%
  ungroup() %>%
  select(-taste_order, -days, -dtp, -rtp) %>%
  tidyr::pivot_longer(cols = c(dt, rt)) %>%
  group_by(record_id, assay_taste, name) %>%
  summarise(
    value = value[time == 4] - value[time == 1]
  ) %>%
  mutate(
    time = 41
  ) %>%
  bind_rows(
    select(ungroup(dtrt_thresholds), -taste_order, -days, -dtp, -rtp) %>%
  tidyr::pivot_longer(cols = c(dt, rt))
  )


hold_for_cors <-  
  hold_thresholds %>%
  filter(time %in% c(1, 41)) %>%
  left_join(
    baseline_vars, by = "record_id"
  )



hold_for_cors %>%
  tidyr::pivot_longer(
    cols = c(age, male, bmi),
    names_to = "baseline_var",
    values_to = "baseline_value"
  ) %>%
  ungroup() %>%
  group_nest(
    time, assay_taste, name, baseline_var
  ) %>%
  mutate(
    cort = purrr::map(
      .x = data,
      .f = ~ cor.test(.x$value, .x$baseline_value)),
    cor_est  = purrr::map_dbl(cort, "estimate"),
    cor_pval = purrr::map_dbl(cort, "p.value"),
    value    = sprintf("%.3f (%.2f)", cor_est, cor_pval)
  ) %>%
  select(-data, -cort, -cor_est, -cor_pval) %>%
  tidyr::pivot_wider(
    id_cols = c(time, assay_taste, name),
    names_from = baseline_var
  ) %>%
  mutate(
    time = if_else(time == 1, "Baseline",
                   "Change from baseline to re-feed")
  ) %>%
  knitr::kable(
    caption = "Correlations between baseline covariates and dectection and recognition thresholds."
  )
```


## Changes in food-liking 

```{r}
flq_completed <- 
  foodliking %>%
  filter(complete.cases(.)) %>%
  group_by(record_id) %>%
  filter(n() == 2) %>%
  ungroup() %>%
  mutate(record_id = as.character(record_id))
```

There were `r length(unique(flq_completed$record_id))` subjects who completed the food-liking questionnaire both before and after the exposure time.

TODO: describe the scoring

Figure XX shows the changes in food-liking.

```{r}
flq_plot <-
  flq_completed %>%
  tidyr::pivot_longer(
    cols = ends_with("flq")
  ) %>%
  mutate(
    name = stringr::str_remove(name, "_flq"),
    name = factor(name, levels = c("salt", "sweet", "fatsalt", "fatsweet"),
                  labels = c("Salt", "Sweet", "Fat & Salt", "Fat & Sweet"))
  ) 

hold <- flq_plot %>%
  tidyr::pivot_wider(
    id_cols = c("record_id", "name"),
    names_from = "time"
  ) %>%
  ungroup() %>%
  group_nest(name) %>%
  mutate(
    ttest = purrr::map(
      .x = data,
      .f = ~ t.test(.x$`0`, .x$`5`, paired = TRUE)
    ),
    tpval = purrr::map_dbl(ttest, "p.value"),
    ttext = sprintf("Paired t-test p-value: %.3f", tpval)
  )

flq_plot %>%
  ggplot(
    data = .,
    aes(x = time, y = value, color = name)
  ) + 
  geom_hline(
    yintercept = 0,
    color = "grey50"
  ) + 
  geom_point(
   alpha = 0.5
  ) +
  geom_line(
    aes(group = record_id),
    size = 0.1,
    alpha = 0.5
  ) +
  geom_text(
    data = hold,
    aes(label = ttext, x = 2, y = 1),
    color = "black",
    size  = 2
  ) +
  stat_smooth(
    # aes(color = assay_taste), 
    method = "lm", se = FALSE
  ) + 
  scale_y_continuous(
    "FLQ Score"
  ) +
  scale_x_continuous(
    "Time",
    breaks = c(0, 5),
    labels = c("Pre", "Post")
  ) +
  scale_color_manual(
    "",
    values = c("#8c75d2", "#11677e", "#d547ca", "#3e3c8d"),
    guide = FALSE
  ) + 
  facet_wrap(
    ~ name,
    ncol = 2
  ) +
  theme_classic() +
  theme(
    strip.background = element_blank(),
    # strip.background.y = element_blank(),
    # strip.text.x  = element_blank(), 
    strip.text.y  = element_text(angle = 0),
    axis.line.x   = element_blank(),
    axis.line.y   = element_line(color = "grey50", size = 0.5),
    axis.ticks.y  = element_line(color = "grey50", size = 0.1),
    axis.ticks.x  = element_line(color = "grey50", size = 0.1),
    axis.text     = element_text(size = 6),
    axis.title.y  = element_text(size = 8),
    axis.title.x  = element_text(size = 8),
    plot.caption  = element_text(size = 6)
  )
```

## Food-liking and Adaptation

```{r flqAdapt}
dtrt_hold <-
  dtrt_thresholds %>%
  ungroup() %>%
  filter(time %in% c(1, 4), record_id %in% flq_completed$record_id) %>%
  select(record_id, time, assay_taste, dt, rt) %>%
  tidyr::pivot_longer(
    cols = c(dt, rt),
    names_to = "threshold"
  ) %>%
  group_by(record_id, assay_taste, threshold) %>%
  summarise(
    dtrt_del = value[time ==4] - value[time == 1]
  ) %>%
  ungroup() %>%
  mutate(
    threshold = factor(threshold, levels = c("dt", "rt"),
                       labels = c("Detection", "Recognition")),
    assay_taste = factor(assay_taste, levels = c("nacl", "sucr"),
                         labels = c("NaCL", "Sucrose"))
  )
  
flq_hold <-
  flq_completed %>%
  ungroup() %>%
  filter(time %in% c(0, 5)) %>%
  tidyr::pivot_longer(
    cols = ends_with("_flq"),
    names_to = "flq_name"
  ) %>%
  group_by(record_id, flq_name) %>%
  summarise(
    flq_del = value[time == 5] - value[time == 0]
  ) %>%
  mutate(
    flq_name = stringr::str_remove(flq_name, "_flq"),
    flq_name = factor(flq_name, levels = c("salt", "sweet", "fatsalt", "fatsweet"),
                  labels = c("Salt", "Sweet", "Fat & Salt", "Fat & Sweet"))
  ) 

plot_hold <-
full_join(
  dtrt_hold,
  flq_hold,
  by = "record_id"
)

# plot_hold %>%
#   group_nest(
#     assay_taste, threshold, flq_name
#   ) %>%
#   mutate(
#     crt = purrr::map(data, ~ cor.test(.x$dtrt_del, .x$flq_del)),
#     cor_est = purrr::map_dbl(crt, "estimate"),
#     cor_p   = purrr::map_dbl(crt, "p.value")
#   ) -> X
  

ggplot(
  data = plot_hold,
  aes(x = dtrt_del, y = flq_del)
) + 
  stat_smooth(
    method = "lm",
    size = 0.5,
    se = TRUE
  ) +
  geom_point(
    aes(color = flq_name),
    alpha = 0.5
  ) +

  scale_color_manual(
    "",
    values = c("#8c75d2", "#11677e", "#d547ca", "#3e3c8d"),
    guide = FALSE
  ) + 
  scale_y_continuous(
    "Change in food liking score"
  ) +
  scale_x_continuous(
    "Change in threshold"
  ) +
  facet_grid(
     flq_name ~ threshold + assay_taste,
    scales = "free"
  ) +   
  theme_classic() +
  theme(
    panel.background = element_rect(fill = "grey90"),
    panel.grid.major  = element_line(color = "white"),
    strip.background = element_blank(),
    # strip.background.y = element_blank(),
    # strip.text.x  = element_blank(), 
    strip.text.y  = element_text(angle = 0),
    # axis.line.x   = element_blank(),
    axis.line.x   = element_line(color = "grey50", size = 0.5),
    axis.line.y   = element_line(color = "grey50", size = 0.5),
    axis.ticks.y  = element_line(color = "grey50", size = 0.1),
    axis.ticks.x  = element_line(color = "grey50", size = 0.1),
    axis.text     = element_text(size = 6),
    axis.title.y  = element_text(size = 8),
    axis.title.x  = element_text(size = 8),
    plot.caption  = element_text(size = 6)
  )
```


# References

